Turbulence in compact to giant H~II regions

### 2022-12-12 strucfunc_paper.tex
Finish new appendix

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{Figures/bright-to-vel-fluct-annotated}
  \caption{
    Toy model of emissivity variations in an ordered velocity field,
    showing co-variation in fractional fluctuations of
    emissivity, \(\sigma_E\),  and surface brightness, \(\sigma_S\)
    together with fluctuations in the plane of sky of the mean velocity,
    \(\sigma\pos\),
    and the mean RMS line width, \(\sigma\los\).
  }
  \label{fig:bright-to-vel-fluct}
\end{figure}

It then follows that the fractional standard deviation of the emissivity
and surface brightness are given by:
\begin{align}
  \label{eq:toy}
  \sigma_E &=
  \frac{
    \biggl[ 3\bigl(\alpha + \alpha^{-1}\bigr)^2 - 4\bigl(1 + \alpha + \alpha^{-1}\bigr)\biggr]^{1/2}
  }{
    2 + \alpha + \alpha^{-1}
  }
  \\
  \sigma_S &=   \frac{\vert\alpha - 1\vert}{1 + \alpha} ,
\end{align}
while the RMS line width and standard deviation of the mean velocities on the plane of the sky
are given by
\begin{align}
  \label{eq:toy}
  \sigma\pos &=\frac{\vert\alpha - 1\vert}{2 (1 + \alpha)}
  \\
  \sigma\los &=   \frac{\alpha^{1/2}}{1 + \alpha}.
\end{align}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{Figures/bright-to-vel-fluct-annotated}
  \caption{
    Toy model of emissivity variations in an ordered velocity field,
    showing co-variation of fractional dispersion of
    emissivity, \(\sigma_E\), and surface brightness, \(\sigma_S\),
    together with plane-of-sky dispersion in mean velocity,
    \(\sigma\pos\),
    and the mean RMS line width, \(\sigma\los\),
    both in units of the inter-layer velocity difference \(\beta\).
  }
  \label{fig:bright-to-vel-fluct}
\end{figure}

It then follows that the fractional standard deviation of the emissivity
and surface brightness are given by:
\begin{align}
  \label{eq:toy}
  \sigma_E &=
  \frac{
    \bigl[ 3\bigl(\alpha + \alpha^{-1}\bigr)^2 - 4\bigl(1 + \alpha + \alpha^{-1}\bigr)\bigr]^{1/2}
  }{
    2 + \alpha + \alpha^{-1}
  }
  \\
  \sigma_S &=   \frac{\vert\alpha - 1\vert}{1 + \alpha} ,
\end{align}
while the RMS line width and standard deviation of the mean velocities on the plane of the sky
are given by
\begin{align}
  \label{eq:toy}
  \sigma\pos &=\frac{\vert\alpha - 1\vert \beta}{2 (1 + \alpha)}
  \\
  \sigma\los &=   \frac{\alpha^{1/2}\beta}{1 + \alpha}.
\end{align}
These are all shown in Figure~\ref{fig:bright-to-vel-fluct} as a function
of the emissivity contrast \(\alpha\).
It can be seen that \(\sigma_E\), \(\sigma_S\), and \(\sigma\pos/\beta\) all increase with \(\alpha\),
reaching asymptotic values of \(\sqrt{3}\), \(1\), and \(0.5\),
respectively as \(\alpha \to \infty\).\footnote{%
  To reach higher relative brightness dispersion \(\sigma_S > 1\) would require
  including more than two lines of sight in the model.
}
The line width \(\sigma\los/\beta\) behaves in the opposite sense, falling from
a maximum value of \(0.5\) when \(\alpha = 0\) towards zero as \(\alpha \to \infty\),
a result of the emission becoming increasingly dominated by one
or the other of the two layers for high emissivity contrast.
The dashed line shows the effect of including a small velocity gradient
within each layer that contributes an additional width of \(\beta/4\),
which is assumed to add in quadrature with \(\sigma\los\).

The predictions of this model are compared with observations in
panel~i of Figure~\ref{fig:brightness-pdfs}.

@@
